Fig 2

### 2020-08-26 analysis/03_datawrangling.Rmd
now with venns in main fig

filteredDEGs <- allDEG %>%
  filter(lfc > 1.1 | lfc < -1.1 ) %>%
  filter(tissue == "hypothalamus")

@@

# chicks
venn.diagram(
  x = list(bldg_n5DEGs, bldg_hatchDEGs, 
           bldg_earlyDEGs,bldg_extendDEGs,  bldg_n9DEGs),
  category.names = c( "N5" ,"Hatch" , "Early", " Extend", "N9"),
  filename = '../figures/venn-chicks-hyp.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  col=c('#3182bd', "#6baed6",  '#cbc9e2', '#6a51a3', '#08519c'),
  fill = c("#3182bd", "#6baed6", "#cbc9e2", '#6a51a3', "#08519c" ),
  main = "Hypothalamus - Nestling Care",
  sub = "Differentially expressesed genes relative to nest building controls"
  )

@@

# chicks
venn.diagram(
  x = list(bldg_inc.d3DEGs, bldg_layDEGs,  bldg_prolongDEGs,
           bldg_inc.d17DEGs, bldg_inc.d9DEGs),
  category.names = c("Inc3" , "Lay" , "Prolong", " Inc17", "Inc9"),
  filename = '../figures/venn-eggs-hyp.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  height = 1500,
	width = 1500,
  col=c( '#78c679', "#fed98e",  '#9e9ac8','#006837', '#31a354'),
  fill = c("#78c679", "#fed98e",  "#9e9ac8",'#006837', "#31a354"),
  main = "Hypothalamus - Incubation",
  sub = "Differentially expressesed genes relative to nest building controls"
  )

```
```{r}
library(cowplot)
eggshyp <- png::readPNG("../figures/venn-eggs-hyp.png")
eggshyp <- ggdraw() +  draw_image(eggshyp, scale = 1)

plot_grid(eggshyp,eggshyp, eggshyp, nrow = 1)
```

>>>>

@@

# chicks
venn.diagram(
  x = list(bldg_n5DEGs, bldg_hatchDEGs, 
           bldg_earlyDEGs,bldg_extendDEGs,  bldg_n9DEGs),
  category.names = c( "N5" ,"Hatch" , "Early", " Extend", "N9"),
  filename = '../figures/venn-chicks-pit.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  height = 1500,
	width = 1750,
  resolution = 500,
  cex = 0.75,
  cat.cex = 0.75,
  col=c('#3182bd', "#6baed6",  '#cbc9e2', '#6a51a3', '#08519c'),
  fill = c("#3182bd", "#6baed6", "#cbc9e2", '#6a51a3', "#08519c" )
  )

@@

# chicks
venn.diagram(
  x = list(bldg_inc.d3DEGs, bldg_layDEGs,  bldg_prolongDEGs,
           bldg_inc.d17DEGs, bldg_inc.d9DEGs),
  category.names = c("Inc3" , "Lay" , "Prolong", " Inc17", "Inc9"),
  filename = '../figures/venn-eggs-pit.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  height = 1500,
	width = 1750,
  resolution = 500,
  cex = 0.75,
  cat.cex = 0.75,
  col=c( '#78c679', "#fed98e",  '#9e9ac8','#006837', '#31a354'),
  fill = c("#78c679", "#fed98e",  "#9e9ac8",'#006837', "#31a354")
  )

### 2020-08-26 analysis/figure-2.Rmd
now with venns in main fig

```{r fig2, fig.width=7.5, fig.height=7.25}
a <- plot.volcano("hypothalamus", sexlevels,  "control_bldg") + 
  facet_wrap(~sex)

@@

g <- plotcandidatechar(hypvsdf, "HTR2C") + labs(subtitle = "Hypothalamus")
h <- plotcandidatechar(hypvsdm, "HTR2C") + labs(y = NULL, x = "") + labs(subtitle = " ")
i <- plotremoval(hypvsdf, "HTR2C")+ labs(y = NULL) + labs(subtitle = " ")
j <- plotremoval(hypvsdm, "HTR2C") + labs(y = NULL, x = "")+ labs(subtitle = " ")
k <- plotreplacement(hypvsdf, "HTR2C") + labs(y = NULL)+ labs(subtitle = " ")
l <- plotreplacement(hypvsdm, "HTR2C") + labs(y = NULL, x = "")+ labs(subtitle = " ")

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("D", "E"), label_size = 8, hjust = 0)
cd <- plot_grid(c,d,rel_widths = c(1.1,1), align = "h",
                labels = c("F", "G"), label_size = 8, hjust = 0)
ef <- plot_grid(e,f,rel_widths = c(1.1,1), align = "h",
                labels = c("H", "I"), label_size = 8, hjust = 0)

ghi <- plot_grid(g,h,i, j,k,l,nrow = 1,
                labels = c("A", "", "B", "", "C"), label_size = 8, hjust = 0,
                rel_widths = c(9,9,8,8,6,6))

fig2 <- plot_grid(ghi,ab,cd,ef,  ncol = 1)
fig2
```

@@

e <- makebargraphv3(DEGremove, "pituitary", "No. of DEGs\n (-)decreased  increased (+)", comparisonlevelsremoval) +
  labs(x = "Offspring removal versus temporal control")
f <- makebargraphv3(DEGreplace, "pituitary", NULL,  comparisonlevelsreplace) +
  labs(x = "Offspring removal versus temporal or external control")

@@

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("D", "E"), label_size = 8, hjust = 0)
cd <- plot_grid(c,d,rel_widths = c(1.1,1), align = "h",
                labels = c("F", "G"), label_size = 8, hjust = 0)
ef <- plot_grid(e,f,rel_widths = c(1.1,1), align = "h",
                labels = c("H", "I"), label_size = 8, hjust = 0)

ghi <- plot_grid(g,h,i, j,k,l,nrow = 1,
                labels = c("A", "", "B", "", "C"), label_size = 8, hjust = 0,
                rel_widths = c(9,9,8,8,6,6))

@@

e <- makebargraphv3(DEGremove, "gonad", "No. of DEGs\n (-)decreased  increased (+)", comparisonlevelsremoval) +
  labs(x = "Offspring removal versus temporal control")
f <- makebargraphv3(DEGreplace, "gonad", NULL,  comparisonlevelsreplace) +
  labs(x = "Offspring removal versus temporal or external control")

@@

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("D", "E"), label_size = 8, hjust = 0)
cd <- plot_grid(c,d,rel_widths = c(1.1,1), align = "h",
                labels = c("F", "G"), label_size = 8, hjust = 0)
ef <- plot_grid(e,f,rel_widths = c(1.1,1), align = "h",
                labels = c("H", "I"), label_size = 8, hjust = 0)

ghi <- plot_grid(g,h,i, j,k,l,nrow = 1,
                labels = c("A", "", "B", "", "C"), label_size = 8, hjust = 0,
                rel_widths = c(9,9,8,8,6,6))

@@

png("../figures/fig4-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig4) 
dev.off()

sessionInfo()
```

>>>>

```{r fig2, fig.width=7.5, fig.height=7.25}
g <- plotcandidatechar(hypvsdf, "HTR2C") + labs(subtitle = "Hypothalamus")
h <- plotcandidatechar(hypvsdm, "HTR2C") + labs(y = NULL, x = "") + labs(subtitle = " ")
i <- plotremoval(hypvsdf, "HTR2C")+ labs(y = NULL) + labs(subtitle = " ")
j <- plotremoval(hypvsdm, "HTR2C") + labs(y = NULL, x = "")+ labs(subtitle = " ")
k <- plotreplacement(hypvsdf, "HTR2C") + labs(y = NULL)+ labs(subtitle = " ")
l <- plotreplacement(hypvsdm, "HTR2C") + labs(y = NULL, x = "")+ labs(subtitle = " ")

a <- plot.volcano("hypothalamus", sexlevels,  "control_bldg") + 
  facet_wrap(~sex)

@@

m <- png::readPNG("../figures/venn-eggs-hyp.png")
m <- ggdraw() +  draw_image(m, scale = 1)

n <- png::readPNG("../figures/venn-chicks-hyp.png")
n <- ggdraw() +  draw_image(n, scale = 1)

ghi <- plot_grid(g,h,k,l,nrow = 1,
                labels = c("A", "", "B"), label_size = 8, hjust = 0,
                rel_widths = c(9,9,6,6))

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("C", "D"), label_size = 8, hjust = 0)

cd <- plot_grid(c,d,rel_widths = c(1.1,1), align = "h",
                labels = c("E", "F"), label_size = 8, hjust = 0)

ef <- plot_grid(f,m,n, rel_widths = c(2,1,1), nrow =1,
                labels = c("G", "H", "I"), label_size = 8, hjust = 0)

fig2 <- plot_grid(ghi,ab,cd,ef,  ncol = 1)
fig2

```

@@

e <- makebargraphv3(DEGremove, "pituitary", "No. of DEGs\n (-)decreased  increased (+)", comparisonlevelsremoval) +
  labs(x = "Offspring removal versus temporal control")
f <- makebargraphv3(DEGreplace, "pituitary", NULL,  comparisonlablelssreplace) +
  labs(x = "Offspring removal versus temporal or external control")

@@

m <- png::readPNG("../figures/venn-eggs-pit.png")
m <- ggdraw() +  draw_image(m, scale = 1)

n <- png::readPNG("../figures/venn-chicks-pit.png")
n <- ggdraw() +  draw_image(n, scale = 1)

ghi <- plot_grid(g,h,k,l,nrow = 1,
                labels = c("A", "", "B"), label_size = 8, hjust = 0,
                rel_widths = c(9,9,6,6))

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("C", "D"), label_size = 8, hjust = 0)

cd <- plot_grid(c,d,rel_widths = c(1.1,1), align = "h",
                labels = c("E", "F"), label_size = 8, hjust = 0)

ef <- plot_grid(f,m,n, rel_widths = c(2,1,1), nrow =1,
                labels = c("G", "H", "I"), label_size = 8, hjust = 0)

@@

e <- makebargraphv3(DEGremove, "gonad", "No. of DEGs\n (-)decreased  increased (+)", comparisonlevelsremoval) +
  labs(x = "Offspring removal versus temporal control")
f <- makebargraphv3(DEGreplace, "gonad", NULL,  comparisonlablelssreplace) +
  labs(x = "Offspring removal versus temporal or external control")

@@

m <- png::readPNG("../figures/venn-eggs-gon.png")
m <- ggdraw() +  draw_image(m, scale = 1)

n <- png::readPNG("../figures/venn-chicks-gon.png")
n <- ggdraw() +  draw_image(n, scale = 1)

ghi <- plot_grid(g,h,k,l,nrow = 1,
                labels = c("A", "", "B"), label_size = 8, hjust = 0,
                rel_widths = c(9,9,6,6))

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("C", "D"), label_size = 8, hjust = 0)

cd <- plot_grid(c,d,rel_widths = c(1.1,1), align = "h",
                labels = c("E", "F"), label_size = 8, hjust = 0)

ef <- plot_grid(f,m,n, rel_widths = c(2,1,1), nrow =1,
                labels = c("G", "H", "I"), label_size = 8, hjust = 0)

@@

png("../figures/fig4-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig4) 
dev.off()
```
